Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-17 manuscript/manuscript.tex
Minor corrections in manuscript

We have developed a Python library that allows us to perform forward gravity computations using tesseroids with variable density in depth.
The code numerically approximates the integral that defines the gravity potential, its gradient and the Marussi tensor through the Gauss-Legendre Quadrature (GLQ).
It essentially consists in approximating the gravity fields of the tesseroids with the effect of point masses located on the scaled nodes of the Legendre polynomials.
We state that this method it's well suited to approximate the effect of tesseroids with arbitrary densities, in contrast with the ones that involves Taylor series expansion.

Although this new code uses only second order GLQ on each integration, we've enhanced its accuracy through a modified adaptive discretization method. It divides the tesseroid by half if the ratio of the distance to the computation point and its size is lower than a predefined distance-size ratio $D$.
We can summarise that $D$ controls the accuracy of the method: a higher value of $D$ generates more divisions of the tesseroids, thou more point masses, what leads to a more precise approximation.

>>>>

We have developed a Python library that allows us to perform forward gravity computations using tesseroids with variable density in depth.
The code numerically approximates the integral that defines the gravity potential, its gradient and the Marussi tensor through the Gauss-Legendre Quadrature (GLQ).
It essentially consists in approximating the gravity fields of the tesseroids with the effect of point masses located on the scaled nodes of the Legendre polynomials.
We state that this method it's well suited to approximate the effect of tesseroids with arbitrary densities, in contrast with the ones that involve Taylor series expansion.

Instead of enhancing the accuracy of the method by increasing the order of the GLQ on each integration, we make use of the modified adaptive discretization algorithm.
It divides the tesseroid by half if the ratio of the distance to the computation point and its size is lower than a predefined distance-size ratio $D$.
We can summarise that $D$ controls the accuracy of the method: a higher value of $D$ generates more divisions of the tesseroids, thus more point masses, what leads to a more precise approximation.
